Measurement Bias from Address Aliasing

### 2016-05-25 presentation.tex
Add picture of memory address space

\begin{itemize}
  \item Identify address aliasing as an underlying explanation for measurement bias.
  \item See how aliasing affects dynamic memory allocation.
  \item Look at opportunities to optimize for aliasing.
\end{itemize}

@@

\begin{itemize}
  \item Runtime performance change from external factors
  \begin{itemize}
    \item Environment variables
    \item Link ordering
  \end{itemize}
  \item Challenge for performance analysis
  \item Effects can invalidate perceived speedup\cite{Mytkowicz:2009:WrongData}
\end{itemize}

@@

  % Some points on hardware perf counters.
  \begin{itemize}
    \item Control execution environment (disable ASLR).
    \item Instrument program using \emph{hardware performance counters}
    \item Python script to iterate over environments.
  \end{itemize}

%todo: Memory layout.

>>>>

\begin{itemize}
  \item Identify address aliasing as an underlying explanation for measurement bias.
  \item See how aliasing affects dynamic memory allocation.
  \item Look at opportunities to optimize for aliasing.
  \item Up to 2x speedup.
\end{itemize}

@@

\begin{itemize}
  \item Runtime performance change from external factors.
  \begin{itemize}
    \item Environment variables
    \item Link ordering
  \end{itemize}
  \item Challenge for performance analysis.
  \item Effects can invalidate perceived speedup~\cite{Mytkowicz:2008:OE&MB}.
\end{itemize}

@@

\begin{columns}[T] % align columns
\begin{column}{.40\textwidth}

  % Some points on hardware perf counters.
  \begin{itemize}
    \item Control execution environment (disable ASLR).
    \item Instrument program using hardware performance counters.
    \item Measure over range of environments.
  \end{itemize}

\end{column}
\begin{column}{.60\textwidth}

\begin{figure}
  \begin{tikzpicture}[font=\footnotesize]
    % See page 453 in pgf manual
    \node [
      rectangle split, rectangle split parts=10, 
      rectangle split part fill={white, white, lightgray, white, lightgray, white, lightgray, white},
      draw, anchor=center, text width=1.8cm
    ] (m) {
        \nodepart{one}
          env. vars
        \nodepart{two}
          stack
        \nodepart{four}
          mmap area
        \nodepart{six}
          heap
        \nodepart{eight}
          bss
        \nodepart{nine}
          data
        \nodepart{ten}
          text
      };
    \draw [decorate, decoration={brace, amplitude=5pt}] (m.south west) -- (m.seven split west) 
      node [black, midway, xshift=-1.5cm, text width=2.0cm] 
        { Program code and static data } ;
    \node[right] at (m.north east)
      { \scriptsize{0x7fff'ffffffff} } ;
    \node[right] at (m.south east)
      { \scriptsize{0x400000} } ;
  \end{tikzpicture}
  \caption{Memory execution context, assuming a 64-bit process running on a Linux system.}
  \label{fig:virtualmemory}
\end{figure}
